Product graphics

### 2009-05-13 product-graphics.tex
The id variable is not the same across years :(
Add some examples of polar plots.  Tweak template names

\documentclass[letterpaper,oneside]{scrartcl}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\usepackage{hyperref}
\usepackage{color}
\definecolor{slateblue}{rgb}{0.07,0.07,0.488}
\hypersetup{colorlinks=true,linkcolor=slateblue,anchorcolor=slateblue,citecolor=slateblue,filecolor=slateblue,urlcolor=slateblue,bookmarksnumbered=true,pdfview=FitB}
\usepackage{url}
\usepackage[round,sectionbib]{natbib}
\bibliographystyle{abbrvnat}
\usepackage[small]{caption2}
\usepackage[small]{titlesec}
\renewcommand\familydefault{bch}

@@

The survey also contains a respondent id variable.  4510 people in sample,  1271 people interviewed only once, 1107 interviewed every year.

@@

\begin{itemize}
  \item {\bf Barchart}: (bars, v/h, width)
  \item {\bf Histogram}: (bars, v/h, 0)
  \item {\bf Stacked} barchart + (bars, h/v, zero)
  \item {\bf Side by side}: (bins, v/h, zero) + barchart  (or possibly spines with width prop to number of bars inside) - that would  give different scales, or use nesting operator with standard barchart
  \item {\bf Spineplot}: (spines, v/h, width)
  \item {\bf Stacked} spineplot: spineplot + (bars, h/v, 0)
  \item {\bf Spinogram}: (spines, v/h, 0)
  \item {\bf Fluctuation} diagram: (flucts, both, total)
  \item {\bf Stacked} fluctuation diagram: fluctuation + (spines, v/h, zero)
  \item {\bf Mosaic} plots: (spines, v/h, width) + (bar, h/v, width) + ... (alternating)
  \item {\bf Double-decker} plot: 
\end{itemize}

@@

Pie charts fall out naturally, as bars in polar coordinates, with angle and radius instead of height and width. Corrections to calculation of area.  .  This is related to the infoslices of \citet{andrews:1998}, which only use half of the disk.  Figure~\ref{fig:polar} shows some examples of product plots in polar coordinates.

@@

\begin{itemize}
  \item Additional info 
  \begin{itemise}
    \item colour (map of the market)
    \item texture (sieve plots)
    \item embedded plots (time series in lab escape)
    \item photographs
    \item text (tables)
  \end{itemise}

>>>>

\documentclass[letterpaper,oneside]{scrartcl}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{plots/}}
\usepackage{hyperref}
\usepackage{url}
\usepackage[round,sectionbib]{natbib}
\bibliographystyle{abbrvnat}
\usepackage[small]{caption2}
\usepackage[small]{titlesec}
\renewcommand\familydefault{bch}

@@

@@

\begin{itemize}
  \item {\bf Stacked} barchart: 1 bar + $n-1$ spines in opposite direction.
  \item {\bf Nested} barchart: $n$ bars.
  \item {\bf Mosaic} plot: spines in alternating directions.  The 1d case has a special name, the spineplot.
  \item {\bf Double-decker} plot: $n-1$ spines + 1 spine in opposite direction.

  \item {\bf Fluctuation} diagram: 
\end{itemize}

@@

Pie charts fall out naturally, as bars in polar coordinates, with angle and radius instead of height and width. And to ensure that counts stay proportional to areas, the square-root is taken of the y-axis. This is related to the infoslices of \citet{andrews:1998}, which only use half of the disk. Figure~\ref{fig:polar} shows some examples of product plots in polar coordinates.

\begin{itemize}
  \item Pie charts
  \item Fourfold displays \citep{friendly:1995}
  \item Bullseye chart
\end{itemize}

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.25\linewidth]{hb-vb-cartesian}%
    \includegraphics[width=0.25\linewidth]{hb-vs-cartesian}%
    \includegraphics[width=0.25\linewidth]{hs-hs-cartesian}%
    \includegraphics[width=0.25\linewidth]{hs-vs-cartesian}

    \includegraphics[width=0.25\linewidth]{hb-vb-polar}%
    \includegraphics[width=0.25\linewidth]{hb-vs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-hs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-vs-polar}
  \caption{}
  \label{fig:polar}
\end{figure}

@@

Labelling these plots is particularly challenging.

\begin{itemize}
  \item Additional info 
  \begin{itemize}
    \item colour (map of the market)
    \item texture (sieve plots)
    \item embedded plots (time series in lab escape)
    \item photographs
    \item text (tables)
  \end{itemize}
